Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-23 writeup/gz_hubble_data.tex
Cheung+15 compared over matched redshift ranges. See #128.
Changes from all annotated PDFs. Closes #108.

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10}, local
environment \citep[such as the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric profiles with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fixed fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
The public availability of more than $10^5$~galaxies in archival imaging across
various studies gives a data sample with the potential for high statistical
significance.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual classifications
to measure galaxies in color-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the classifications collected from the Galaxy Zoo Hubble
(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
phase of Galaxy Zoo, following its initial results classifying
$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
classification scheme that included bars, spiral arms, and galactic bulges
\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
for the first time on images of high-redshift galaxies taken with \hst. The
Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
high redshift, but using ACS and WFC3 rest-frame infrared imaging (Simmons
et~al., submitted).

@@

The project includes images from the Sloan Digital Sky Survey
\citep[SDSS;][]{yor00,str02}, in particular those from Data~Release~7
\citep{aba09}. A small number of images were used in the creation of simulated
\hst{} images, described in Sections \ref{ssec:ferengi} and \ref{sec:debiasing}
below; the majority of SDSS images used in GZH were from Stripe~82. The
Stripe~82 samples in GZH include single-epoch and co-added images, intended to
facilitate comparison of morphological classification with image depth.

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift (out to at least $z\sim1-2$). The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes (i.e., $e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disc features with increasing redshift
for two galaxies with $e=0$.

The final number of \ferengi{} images produced for each galaxy is ultimately a
function of galaxy's redshift (since the new images cannot be resampled at
better angular resolution than the original SDSS data), as well as the number
of $e$ values selected. The use of these images to correct for redshift-dependent
bias is described in Section \ref{sec:debiasing}.

@@

\subsection{Image creation}\label{ssec:images}

The images used for classification in GZH were color-composite JPEGs made from
multi-band data. These were created followed the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centers. The relative scalings of the filter bands were
chosen while trying to reproduce the color appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the two. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

@@

The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
launch.  These galaxies used ``pseudocolor'' images created by using
the ACS \Iband{} data as an illumination map and ground-based imaging from the
\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
information (see \citealt{gri12} for further details). This resulted in images
with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
overall intensity, but color gradients at ground-based resolution, with seeing
between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

@@

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masked procedure was effective in preserving the color balance for
galaxies, retaining the visibility of faint features while reducing the color
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding Task numbers. Tasks in the decision tree are color-coded by
tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks colored green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree.}
\label{fig:decisiontree}
\end{figure*}

@@

The GZH decision tree was designed to remain close to that used by GZ2 while
taking account of the likely differences in high redshift systems, and has four
broad sets of morphologies classified by the users.  The first option
designated stars or image artifacts (the result of either bad data or incorrect
identification as a galaxy by the ACS pipeline); in this case, the
classification process ended and no further questions were asked. The second
set was smooth galaxies, intended to select ellipticals/early-types;
volunteers also indicate the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which measured the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of images
from AEGIS, GEMS, and GOODS that were previously excluded from the original
sample due to cuts on blended and/or saturated objects and subsequently
confirmed as classifiable galaxies. The GZH site collected data until its
replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 on the
fourth version of the Galaxy~Zoo site. The GZH project had a total of
10,349,357~classifications from 93,898 registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $(w)$ was 1 for the top 95\% of classifiers, as ranked by consistency.
For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
effectively zero for the bottom 1\% in the distribution function. Since this
only affected a tiny percentage of the classifiers (and an even smaller
percentage of the classifications) the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.
% would be good to quantify "tiny" and "even smaller [than tiny]"

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin11,wil13} were based on observations of galaxies in the Sloan Digital
Sky Survey (SDSS), which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the morphological distribution
were due to a redshift-dependent bias that affects image quality and
classification accuracy (\ie, galaxies of a given mass/size will appear smaller
and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
technique; its dependence in data quality is a potential problem for
\emph{both} automated and visual classifications, and must be addressed in
order to accurately measure demographics over any significant redshift range.

For both previous releases of Galaxy~Zoo morphologies, a correction for
redshift-dependent bias was applied based on matching the classification
fractions at the highest redshifts with those at the lowest redshift.
\citet{bam09} and \citet{wil13} provide complete descriptions of the process
for GZ1 and GZ2, respectively.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
values. The color histogram shows the number of \ferengi{} images as a function
of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
with contours starting at $N=1000$ and separated by intervals of 1000 up to
7000.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the
lowest redshift in the \ferengi{} bins ($z=0.3$). Here, $\zeta$ is a model
parameter that controls the rate at which \ffeatures{} decreases with increasing
redshift (and that may depend on other galaxy properties). This formula fits
the data relatively well (with very few exceptions, the vote fractions for
featured galaxies decrease monotonically with increasing redshift), and the
exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$
and zero. Figure~\ref{fig:zeta_examples} shows the change in vote fraction and
the best-fit model for a random sample of galaxies.

@@

Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
function of surface brightness. Higher-surface brightness galaxies have
slightly stronger average corrections, possibly because these galaxies are more
likely to have larger $f_\textrm{features}$ values at high redshifts. Low
surface brightness galaxies are more likely to begin low and remain low; the
bounded nature of the dropoff (and variance among the individual voters) means
that the average magnitude of $\zeta$ will be lower.

@@

\begin{equation}
f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}.
\label{eqn:fzeta_mod}
\end{equation}

@@

Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
\ffeaturesrest{} is \emph{not} always single valued; hence, it is not
appropriate to correct galaxies that lie in certain regions of surface
brightness/redshift/\ffeatures{} space. These regions tend to have low
\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
These regions contain two morphological types of galaxies: the first set are
genuine ellipticals, which have low values of \ffeatures{} at both high and low
redshift. The second group are disks whose features become indistinct at high
redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
the value observed at high redshift is very low. This effect is strongest at
high $z$ and low $\mu$, where features become nearly impossible to discern in
the images (see top right panel of Figure~\ref{fig:f_vs_f}).

>>>>

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10}, local
environment \citep[\eg, the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric galaxies with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

@@

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
However, the public availability of more than $10^5$~galaxies in archival
imaging has generated a data sample with the potential
for statistically-robust studies of galaxy demographics and evolution.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration (e.g., see \citealt{lah95} for a discussion on the extent to which
eight expert classifiers agree with each other). Automated measurements, both
parametric \citep{pen02a,sim11,lac12} and non-parametric
\citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample
sizes, but do not always fully capture the relevant features, especially for
asymmetric galaxies that become increasingly common at high redshifts. The
Galaxy Zoo project \citep{lin08,for12} utilizes crowdsourced visual classifications
to measure galaxies in color-composite images. The efforts of more than
$2\times10^5$~classifiers allow for multiple independent classifications of
each image which are combined and calibrated to give a distribution of vote
fractions proportional to the probability of a feature being visible. While
crowdsourced data require extensive calibration \citep{bam09,wil13}, they have
a proven reliability and have been used for a wide variety of scientific
studies \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the classifications collected from the Galaxy Zoo Hubble
(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
phase of Galaxy Zoo, following its initial results classifying
$\sim900,000$ Sloan Digital Sky Survey (SDSS)~images into primarily early/late~types \citep{lin11} and
Galaxy~Zoo~2, which covered a subset of $\sim250,000$~images using a more detailed
classification scheme that included bars, spiral arms, and galactic bulges
\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
for the first time on images of high-redshift galaxies taken with \hst. The
Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
high redshift, but using ACS and WFC3 rest-frame infrared imaging (Simmons
et~al., submitted).

@@

The project includes images from the SDSS \citep{yor00,str02}, in particular
those from Data~Release~7 \citep{aba09}. A small number of images were used in
the creation of simulated \hst{} images, described in Sections
\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images
used in GZH were from Stripe~82. The Stripe~82 samples in GZH include
single-epoch and co-added images. The single-epoch images provide a local
sample for comparison to higher-redshift galaxies (including the new
measurments of clumpy structure), while the co-added images allow for analysis
of morphological properties as a function of image depth.

%The creation of 51,861 images from these sources is described in Section
%\ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites created using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
\stripe{} images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in the reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

In addition to the physical parameters of the input images, the \ferengi{}
output depends on assumptions of the global galaxy evolution model. This
evolution is a crude mechanism that mimics the brightness increase of galaxies
with increasing redshift \citep[\eg,][]{lil98,lov12}. The effect on the
redshifted images is simply an empirical addition to the magnitude of a galaxy
of the form $M' = e\times z + M$, where $M'$ is the corrected magnitude, and
$e$ is the evolutionary correction in magnitudes ($e=-1$ essentially
brightens the entire galaxy by 1~magnitude by $z=1$). \ferengi{} was run on the images
for values of $e$ starting from $e=0$ and decreasing to $e=-3.5$ in increments
of $\Delta e = 0.5$. Figure~\ref{fig:exampleFERENGI} shows several examples
of the effects of ``losing'' spiral/disc features with increasing redshift
for two galaxies with no evolution corrections ($e=0$); as the signal-to-noise ratio in the images
decreases and the galaxies become fainter, the contrast between features
like spiral arms goes down and \ffeatures{} drops to the point where both
galaxies would have been classified as likely ellipticals.

The final number of \ferengi{} images produced for each galaxy is ultimately a
function of the galaxy's redshift (since the new images cannot be resampled at
better angular resolution than the original SDSS data), as well as the number
of $e$ values selected. The use of these images to correct for redshift-dependent
bias is described in Section \ref{sec:debiasing}.

@@

\subsection{Creating color images}\label{ssec:images}

The images used for classification in GZH were color-composite JPEGs made from
multi-band data. These were created following the method of \citet{lup04}, which
preserves color information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centers. The relative scalings of the filter bands were
chosen while trying to reproduce the color appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided \hst{} images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the two. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

@@

The COSMOS survey provides only \Iband{} HST imaging. For these galaxies, GZH
used ``pseudocolor'' images created by using the ACS \Iband{} data as an
illumination map and ground-based imaging from the \subaru{} telescope in
$B_J$, $r^+$, and $i^+$ filters to provide color information (see
\citealt{gri12} for further details). This resulted in images with the angular
resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but
color gradients at ground-based resolution, with seeing between 0.95\arcsec{}
and 1.05\arcsec{} \citep{tan07}.

@@

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masking procedure was effective in preserving the color balance for
galaxies and retained the visibility of faint features, while reducing the color
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/gzh_decision_tree.pdf}
\caption{Flowchart of the questions presented to GZH classifiers, labeled with
the corresponding Task numbers. Tasks in the decision tree are color-coded by
tier level: Gray-colored Tasks are 1$^\mathrm{st}$-tier questions which are
asked in every classification. Tasks colored green, blue, purple, and pink
(respectively) are one, two, three, or four steps below branching points in the
decision tree. The dashed line between T15 and T03 indicates the unique case
where volunteers could label both clumpy and disk-like morphologies for
galaxies with clumps arranged in a spiral pattern.}
\label{fig:decisiontree}
\end{figure*}

@@

The GZH decision tree was designed to remain close to that used by GZ2 while
taking account of the likely differences in high redshift systems, and has four
broad sets of morphologies classified by the users.  The first set
identified stars or image artifacts (the result of either bad data or incorrect
identification as a galaxy by the ACS pipeline); in this case, the
classification process ended and no further questions were asked. The second
set was smooth galaxies, intended to select ellipticals/early-types;
volunteers also indicate the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which labeled the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

@@

The GZH project was launched on 23~Apr~2010 with the inclusion of the AEGIS,
GEMS, GOODS 2-epoch, and SDSS Stripe~82 images. Images from COSMOS and the
simulated AGN were activated in Dec 2010, as well as a small sample of images
from AEGIS, GEMS, and GOODS that were previously excluded from the original
sample due to cuts on blended and/or saturated objects and subsequently
confirmed as classifiable galaxies. The GZH site collected data until its
replacement, the fourth phase of
Galaxy~Zoo\footnote{\url{http://zoo4.galaxyzoo.org}} (including data from both
the \hst{} CANDELS survey and SDSS DR8) began on 10~Sep~2012. Classifications
for the GOODS 5-epoch images were separately obtained from Mar-Jun 2015 using
the fourth version of the Galaxy~Zoo site and the same GZH decision tree.
The GZH project had a total of 10,349,357~classifications from
93,898~registered participants. 
% Sum is the total of the GZH SQL table plus the GOODS full-depth imaging in GZ4.

@@

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar to that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $w$ was 1 for the top 95\% of classifiers, as ranked by consistency.
For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
effectively zero for the bottom 1\% in the distribution function. Since
downweighting only occurs for the bottom few percent of classifiers (and an even smaller
percentage of the classifications), the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin11,wil13} were based on observations of galaxies in the SDSS,
which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the morphological distribution
were due to a redshift-dependent bias that affects image quality and
classification accuracy (\ie, galaxies of a given mass/size will appear smaller
and dimmer at higher redshifts).  This bias is not unique to the crowdsourcing
technique; its dependence in data quality is a potential problem for
\emph{both} automated and visual classifications, and must be addressed in
order to accurately measure demographics over any significant redshift range.

For both previous releases of Galaxy~Zoo morphologies, a correction for
redshift-dependent bias was applied based on matching the mean classification
fractions at the highest redshifts with those at the lowest redshift.
\citet{bam09} and \citet{wil13} provide complete descriptions of the process
for GZ1 and GZ2, respectively.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/sb_redshift.pdf}
\caption{Surface brightness as a function of redshift for 3,950~\ferengi{}
images and the 102,548~galaxies in the ACS sample with measured $\mu$ and $z$
values. The color histogram shows the number of \ferengi{} images as a function
of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample,
with contours starting at $N=1000$ and separated by intervals of 1000 up to
7000.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

\noindent where $f_{\mu,z=0.3}$ is the vote fraction at the
lowest redshift in the \ferengi{} bins ($z_0=0.3$). Here, $\zeta$ is a model
parameter that controls the rate at which \ffeatures{} decreases with increasing
redshift (and that may depend on other galaxy properties). This formula fits
the data relatively well (with very few exceptions, the vote fractions for
featured galaxies decrease monotonically with increasing redshift), and the
exponential function bounds the observed vote fractions between $f_{\mu,z=0.3}$
and zero. Figure~\ref{fig:zeta_examples} shows the change in vote fraction and
the best-fit model for a random sample of galaxies.

@@

Figure~\ref{fig:zeta_mu} examines the results of fitting the \ferengi{} images
with Equation~\ref{eqn:fzeta}. Interestingly, the correction is only a weak
function of surface brightness. Higher-surface brightness galaxies have on
average slightly stronger corrections, possibly because these galaxies have
larger $f_\textrm{features}$ values at high redshifts. Low surface brightness
galaxies are more likely to begin low and remain low; the bounded nature of the
dropoff (and variance among the individual voters) means that the average
magnitude of $\zeta$ will be lower.

@@

\begin{equation}
f_\textrm{features,debiased} = 1 - (1 - f_\mathrm{features,weighted})e^{\frac{z-z_0}{\hat\zeta}}
\label{eqn:fzeta_mod}
\end{equation}

\noindent where $f_\mathrm{features,weighted}$ is the weighted vote fraction
described in Section~\ref{ssec:weighting}.

@@

Figure~\ref{fig:f_vs_f} shows that the relationship between \ffeaturesz{} and
\ffeaturesrest{} is \emph{not} always single-valued; hence, it is not
appropriate to correct galaxies that lie in certain regions of surface
brightness/redshift/\ffeatures{} space. These regions tend to have low
\ffeatures{} values at high redshift, but a wide range of values at $z=0.3$.
These regions contain two morphological types of galaxies: the first set are
genuine ellipticals, which have low values of \ffeatures{} at both high and low
redshift. The second group are disks whose features become indistinct at high
redshift; hence their \ffeatures{} value at $z=0.3$ may be quite high, while
the value observed at high redshift is very low. This effect is strongest at
high $z$ and low $\mu$, where features become nearly impossible to discern in
the images (see top right panel of Figure~\ref{fig:f_vs_f}).
